SPECS-decadal-MOS

### 2017-09-20 CixPAG/spell-statistics.Rmd

## Spell sttatistics

@@

@@

### Prepare rthe preictand

```{r, fig.width=8, fig.height=8}
pca.lws <- PCA(pcafill(lws.jja),n=5)
pca.tmax <- PCA(pcafill(tmax.jja),n=5)
plot(pca.lws,new=FALSE)
plot(pca.tmax,new=FALSE)
```

```{r}
if (!file.exists("dse.tmax.india.rda")) {
  T2m <- subset(as.4seasons(retrieve("~/Downloads//air.mon.mean.nc",lon=c(65,95),lat=c(5,27))),it='jja')
  dse.tmax.india <- DSensemble.pca(pca.tmax,predictor=T2m,biascorrect = TRUE,ip=1:4)
  save(dse.tmax.india,file="dse.tmax.india.rda")
} else load("dse.tmax.india.rda")

@@

```{r, warning=FALSE, message=FALSE, fig.width=8, fig.height=8}
## Script that reads European temperature data and explores the connection between 
## the seasonal mean temperature and the mean length of the warm/cold spells 
it <- 'jja'
if (it =='djf') {
  cold <- TRUE
  threshold <- 0
  is <- 2
} else {
  cold <- FALSE
  threshold <- 20
  is <- 1
}

@@

    ## Compare the spell-distribution with a geometric distribution
    q.spell[i,] <- quantile(subset(subset(s,is=is),it=it),probs=seq(0.05,0.95,by=0.1),na.rm=TRUE)
    q.geom[i,] <- qgeom(p=seq(0.05,0.95,by=0.1),prob=1/y[i])
    std[i] <- sd(subset(z,it=it),na.rm=TRUE)
    x[i] <- mean(subset(z,it=it),na.rm=TRUE)
    }
  }
  save(x,y,s,std,q.spell,q.geom,file=paste('ecad.tg.',it,'.rda',sep=''))
} else load(paste('ecad.tg.',it,'.rda',sep=''))
## Plot results

plot(x,y,main=paste('Mean',it,'temperature & mean length of intervals',
                    c('below','above')[c(cold,!cold)],threshold,'C'),
     sub='source: ECA&D',pch=19,col=rgb(0.5,0,0,0.3),
     xlab=expression(bar(T)),ylab=expression(bar(tau)))
grid()

@@

## Test if the spell length statistics is close to geometric
plot(c(q.spell),c(q.geom),main='Spell length statistics & the geometric distribution',
     xlim=range(q.spell,q.geom,na.rm=TRUE),
     ylim=range(q.spell,q.geom,na.rm=TRUE),pch=19,col=rgb(0,0,0,0.2),
     xlab=expression(q[p]),ylab='qgeom(p,1/mean)')
grid()
lines(range(q.spell,q.geom,na.rm=TRUE),range(q.spell,q.geom,na.rm=TRUE),col='red')

>>>>

## Spell statistics

@@

The mean summer daily maximum temperature and the length of summer-time warm spells.

@@

### Prepare the predictand

```{r, fig.width=8, fig.height=8}
pca.lws <- PCA(pcafill(lws.jja),n=5)
plot(pca.lws,new=FALSE)
```

```{r, fig.width=8, fig.height=8}
pca.tmax <- PCA(pcafill(tmax.jja),n=5)
plot(pca.tmax,new=FALSE)
```

```{r}
if (!file.exists("dse.tmax.india.rda")) {
  T2m <- subset(as.4seasons(retrieve("~/Downloads//air.mon.mean.nc",lon=c(65,95),lat=c(5,27))),it='jja')
  dse.tmax.india <- DSensemble.pca(pca.tmax,predictor=T2m,biascorrect = TRUE,ip=1:4)
  save(dse.tmax.india,file="dse.tmax.india.rda")
} else load("dse.tmax.india.rda")
```

@@

```{r, warning=FALSE, message=FALSE, fig.width=8, fig.height=8}
## Script that reads European temperature data and explores the connection between 
## the seasonal mean temperature and the mean length of the warm/cold spells 
it <- 'jja'
if (it =='djf') {
  cold <- TRUE
  threshold <- 0
  is <- 2
} else {
  cold <- FALSE
  threshold <- 20
  is <- 1
}
```

```{r}

@@

    ## Compare the spell-distribution with a geometric distribution
    q.spell[i,] <- quantile(subset(subset(s,is=is),it=it),probs=seq(0.05,0.95,by=0.1),na.rm=TRUE)
    q.geom[i,] <- qgeom(p=seq(0.05,0.95,by=0.1),prob=1/y[i])
    std[i] <- sd(subset(z,it=it),na.rm=TRUE)
    x[i] <- mean(subset(z,it=it),na.rm=TRUE)
    }
  }
  save(x,y,s,std,q.spell,q.geom,file=paste('ecad.tg.',it,'.rda',sep=''))
} else load(paste('ecad.tg.',it,'.rda',sep=''))
## Plot results
```

```{r}
plot(x,y,main=paste('Mean',it,'temperature & mean length of intervals',
                    c('below','above')[c(cold,!cold)],threshold,'C'),
     sub='source: ECA&D',pch=19,col=rgb(0.5,0,0,0.3),
     xlab=expression(bar(T)),ylab=expression(bar(tau)))
grid()

@@

## Test if the spell length statistics is close to geometric
plot(c(q.spell),c(q.geom),main='Spell length statistics & the geometric distribution',
     xlim=range(q.spell,q.geom,na.rm=TRUE),
     ylim=range(q.spell,q.geom,na.rm=TRUE),pch=19,col=rgb(0,0,0,0.2),
     xlab=expression(q[p]),ylab='qgeom(p,1/mean)')
grid()
lines(range(q.spell,q.geom,na.rm=TRUE),range(q.spell,q.geom,na.rm=TRUE),col='red')
```

### 2017-09-20 EU-Circle/eu-circle_case-study-1.Rmd

```{r}
eof.dry <- subset(eof.dry,ip=1:4)
```

@@

```{r, height=8}
plot(ds.ataf.dry,new=FALSE)
```

@@

```{r, height=8}
plot(ds.ataf.t2m,new=FALSE)
```

@@

```{r, height=8}
plot(ds.ataf.slp,new=FALSE)
```

@@

```{r}
## Convert the projected data into an EOF for the multi-model ensemble
eof.dry.z <- as.eof(dse.mld.slp)
## Use this EOF as input with the downscaling model calibrated with mean dry interval duration to make projections of ln(fire area)
ds.Af <- exp(predict(ds.ataf.dry,newdata=eof.dry.z))
plot(ds.Af,new=FALSE)
```

>>>>

```{r}
eof.dry <- subset(eof.dry,ip=1:4)
index(eof.dry) <- year(eof.dry)
```

@@

```{r, fig.height=8}
plot(ds.ataf.dry,new=FALSE)
```

@@

```{r, fig.height=8}
plot(ds.ataf.t2m,new=FALSE)
```

@@

```{r, fig.height=8}
plot(ds.ataf.slp,new=FALSE)
```

@@

```{r, fig.height=8}
## Convert the projected data into an EOF for the multi-model ensemble
eof.dry.z <- as.eof(dse.mld.slp)
## Use this EOF as input with the downscaling model calibrated with mean dry interval duration to make projections of ln(fire area)
ds.Af <- exp(predict(ds.ataf.dry,newdata=eof.dry.z))
plot(ds.Af,new=FALSE)
```

### 2017-09-20 EU-Circle/eu-circle_case-study-5.Rmd

```{r}
library(esd)
ss <- select.station(param='precip',cntr='Germany',alt=250,nmin=75)
map(ss,new=FALSE)
Y <- station(ss)
Y <- subset(Y,it=c(1950,2015))
diagnose(Y)
nv <- apply(coredata(Y),2,'nv')
Y <- subset(Y,is=nv > 24000)
```

@@

```{r}
rr <- retrieve('data.ECAD/rr_0.25deg_reg.nc',lon=range(lon(Y)),lat=range(lat(Y)))
map(rr,new=FALSE)
Arr <- aggregate.area(rr)
plot(rr,new=FALSE)
```

>>>>

```{r rain-gauges}
library(esd)
ss <- select.station(param='precip',cntr='Germany',alt=250,nmin=75)
map(ss,new=FALSE)
Y <- station(ss)
Y <- subset(Y,it=c(1950,2015))
diagnose(Y)
nv <- apply(coredata(Y),2,'nv')
Y <- subset(Y,is=nv > 24000)
```

@@

```{r}
rr <- retrieve('~/storeB/data/data.ECAD/rr_0.25deg_reg.nc',lon=range(lon(Y)),lat=range(lat(Y)))
map(rr,new=FALSE)
Arr <- aggregate.area(rr)
plot(rr,new=FALSE)
```

### 2017-09-20 SPECS/specs-decade-mos.Rmd

print('Get the predictands: mu & fw from EOBS')
if (!file.exists('~/mu_0.25deg_reg.nc'))
  mu.eobs <-  wetdaymean('~/data/data.ECAD/rr_0.25deg_reg.nc') else
  mu.eobs <- retrieve('~/mu_0.25deg_reg.nc')
fw.eobs <- retrieve('~/fw_0.25deg_reg.nc')
attr(mu.eobs,'variable') <- 'mu'
attr(fw.eobs,'variable') <- 'fw'
attr(fw.eobs,'unit') <- 'fraction'
#index(fw.eobs) <- year(as.Date(time,origin = as.Date("1950-01-01")))
#index(mu.eobs) <- year(as.Date(time,origin = as.Date("1950-01-01")))
```

>>>>

print('Get the predictands: mu & fw from EOBS')
if (!file.exists('~/mu_0.25deg_reg.nc'))
  mu.eobs <-  wetdaymean('~/data/data.ECAD/rr_0.25deg_reg.nc') else
  mu.eobs <- retrieve('~/mu_0.25deg_reg.nc')
fw.eobs <- retrieve('~/fw_0.25deg_reg.nc')
attr(mu.eobs,'variable') <- 'mu'
attr(fw.eobs,'variable') <- 'fw'
attr(mu.eobs,'source') <- 'EOBS'
attr(fw.eobs,'source') <- 'EOBS'
attr(fw.eobs,'unit') <- 'fraction'
#index(fw.eobs) <- year(as.Date(time,origin = as.Date("1950-01-01")))
#index(mu.eobs) <- year(as.Date(time,origin = as.Date("1950-01-01")))
```
